A mechanization of semi-simplicial and semi-cubical sets in the calculus of inductive constructions

### 2022-08-29 paper/paper.tex
paper: fix alignmented of iter-param diagram

A full 2-cube is made of two full 1-cubes connected by a lifted 1-cube made of two lines connecting the former points and a square connecting the former lines:
\begin{equation*}
  \begin{array}{l}
    \begin{array}{lll}
      \mbox{\textit{squares}}     \\
      [3mm]\mbox{\textit{lines}}  \\
      [3mm]\mbox{\textit{points}} \\
      [1mm]\end{array}
    \framebox{$\begin{array}{lll}
                     \overbrace{\raisebox{0.05cm}{\framebox{$
                           \begin{array}{ll}
                  \raisebox{0cm}{\hspace{.5cm}{\scriptsize$\mylayer[1][0]$}} & \framebox{$a_{0\unitpoint}$} \\
                  [1mm]\overbrace{\framebox{$a_{00}$}~\framebox{$a_{01}$}}   &
                  \raisebox{-0.1cm}{{\scriptsize \hspace{0.1cm}$\myfiller[1][0]\!\!\!\!\!\!\!\!$}}
                  \\
                \end{array}
                         $}}~
                     {\raisebox{0.05cm}{\framebox{$
                           \begin{array}{ll}
                  \raisebox{0cm}{\hspace{.5cm}{\scriptsize$\mylayer[1][0]$}} & \framebox{$a_{1\unitpoint}$} \\
                  [1mm]\overbrace{\framebox{$a_{10}$}~\framebox{$a_{11}$}}   &
                  \raisebox{-0.1cm}{{\scriptsize \hspace{0.1cm}$\myfiller[1][0]\!\!\!\!\!\!\!\!$}}
                \end{array}
                         $}}}}^{\mylayer[2][0]}~\stackrel{\raisebox{9.5mm}{$\framebox{$
                               \begin{array}{ll}
                      \raisebox{0cm}{\hspace{.5cm}{\scriptsize$\mylayer[2][1]$}}                   & \framebox{$a_{\unitpoint\unitpoint}$} \\
                      [1mm]\overbrace{\framebox{$a_{\unitpoint 0}$}~\framebox{$a_{\unitpoint 1}$}} &
                      \raisebox{-0.1cm}{{\scriptsize \hspace{0.1cm}$\myfiller[2][1]\!\!\!\!\!\!\!\!$}}
                    \end{array}$}$}}
                     {\raisebox{-0.4cm}{{\scriptsize \hspace{2.5cm}$\myfiller[2][0]\!\!\!\!\!\!\!$}}}
                   \end{array}$}
    ~~~\parbox{3.5cm}{{\it additionally, each atomic component at dimension $n$ is a $\myfiller[n][n]$}} \\
    [-1mm]\qquad\qquad~~
    \begin{tikzcd}
      \bullet\arrow[r, leftrightarrow] & \bullet\\
    \end{tikzcd}
    \mbox{\normalsize $\myframe[1][1]$}
    \quad~~
    \begin{tikzcd}
      \bullet\arrow[r, leftrightarrow] & \bullet \\
    \end{tikzcd}
    \mbox{\normalsize $\myframe[1][1]$}                                                                  \\
    [-2mm]\qquad\qquad
    \begin{tikzcd}
      \bullet\arrow[r, leftrightarrow] & \bullet\\
    \end{tikzcd}
    \mbox{\normalsize$\myframe[2][1]$}                                                                   \\
    [-2mm]\qquad\qquad
    \begin{tikzcd}
      \bullet\arrow[r, leftrightarrow] & \bullet\\
    \end{tikzcd}
    \mbox{\normalsize$\myframe[2][2]$}                                                                   \\
  \end{array}
\end{equation*}

>>>>

A full 2-cube is made of two full 1-cubes connected by a lifted 1-cube made of two lines connecting the former points and a square connecting the former lines:
{\scriptsize
\begin{equation*}
  \begin{array}{l}
    \begin{array}{lll}
      \mbox{\textit{squares}}     \\
      [3mm]\mbox{\textit{lines}}  \\
      [3mm]\mbox{\textit{points}} \\
      [1mm]\end{array}
    \framebox{$\begin{array}{lll}
                     \overbrace{\raisebox{0.05cm}{\framebox{$
                           \begin{array}{ll}
                  \raisebox{0cm}{\hspace{.5cm}{\mylayer[1][0]}} & \framebox{$a_{0\unitpoint}$} \\
                  [1mm]\overbrace{\framebox{$a_{00}$}~\framebox{$a_{01}$}}   &
                  \raisebox{-0.1cm}{\hspace{0.1cm}\myfiller[1][0]\!\!\!\!\!\!\!\!}
                  \\
                \end{array}
                         $}}~
                     {\raisebox{0.05cm}{\framebox{$
                           \begin{array}{ll}
                  \raisebox{0cm}{\hspace{.5cm}{\mylayer[1][0]}} & \framebox{$a_{1\unitpoint}$} \\
                  [1mm]\overbrace{\framebox{$a_{10}$}~\framebox{$a_{11}$}}   &
                  \raisebox{-0.1cm}{\myfiller[1][0]\!\!\!\!\!\!\!\!}
                \end{array}
                         $}}}}^{\mylayer[2][0]}~\stackrel{\raisebox{9.5mm}{$\framebox{$
                               \begin{array}{ll}
                      \raisebox{0cm}{\hspace{.5cm}{$\mylayer[2][1]$}}                   & \framebox{$a_{\unitpoint\unitpoint}$} \\
                      [1mm]\overbrace{\framebox{$a_{\unitpoint 0}$}~\framebox{$a_{\unitpoint 1}$}} &
                      \raisebox{-0.1cm}{ \hspace{0.1cm}\myfiller[2][1]\!\!\!\!\!\!\!\!}
                    \end{array}$}$}}
                     {\raisebox{-0.4cm}{\hspace{2.5cm}\myfiller[2][0]\!\!\!\!\!\!\!}}
                   \end{array}$}
    ~~~\parbox{2cm}{{\it additionally, each atomic component at dimension $n$ is a \myfiller[n][n]}} \\\\
    [-1mm]\qquad\qquad\quad~~
    \begin{tikzcd}[column sep=5.2em, row sep=1em]
      \phantom{\bullet}\arrow[r, leftrightarrow] & \phantom{\bullet}
    \end{tikzcd}
    \mbox{\myframe[1][1]}
    \qquad
    \begin{tikzcd}[column sep=5.2em, row sep=1em]
      \phantom{\bullet}\arrow[r, leftrightarrow] & \phantom{\bullet}
    \end{tikzcd}
    \mbox{\myframe[1][1]} \\
    \qquad\qquad~~
    \begin{tikzcd}[column sep=32em, row sep=1em]
      \phantom{\bullet}\arrow[r, leftrightarrow] & \phantom{\bullet}
    \end{tikzcd}
    \mbox{\myframe[2][1]} \\
    \qquad\qquad~~
    \begin{tikzcd}[column sep=39em, row sep=1em]
      \phantom{\bullet}\arrow[r, leftrightarrow] & \phantom{\bullet}
    \end{tikzcd}
    \mbox{\myframe[2][2]} \\
  \end{array}
\end{equation*}
}
